---
output: github_document
---
[![build](https://github.com/zichun-xu/bis620/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zichun-xu/bis620/actions/workflows/R-CMD-check.yaml)
[![lint](https://github.com/zichun-xu/bis620/actions/workflows/lint.yaml/badge.svg)](https://github.com/zichun-xu/bis620/actions/workflows/lint.yaml)
[![test-coverage](https://github.com/zichun-xu/bis620/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/zichun-xu/bis620/actions/workflows/test-coverage.yaml)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2022

<!-- badges: start -->
<!-- badges: end -->

The goal of bis620.2022 is to produce exploratory analysis tools for the UK Biobank accelerometry data, including:\
a. time series plot\
b. spectral signature calculation

## Installation

You can install the development version of bis620.2022 from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
devtools::install_github("zichun-xu/bis620")
```

## Example

1. Load the UK Biobank accelerometry data
```{r}
library(bis620.2022)
data("ukb_accel")
```

2. Time series plots of the data:
```{r}
accel_plot(ukb_accel)
```

3. Calculate the spectral signature of the Data
```{r}
spectral_signature(ukb_accel)
```

## Links to Actions
#### 1. Test Coverage: https://github.com/zichun-xu/bis620/actions/workflows/test-coverage.yaml
#### 2. lint: https://github.com/zichun-xu/bis620/actions/workflows/lint.yaml
